Towards human SuperEEG

### 2018-10-06 paper/main.tex
backing up progress on results section [WIP]

\newcommand{\taskrecon}{S1}
\newcommand{\perexptaskrecon}{S2}
\newcommand{\perexpcorrmaps}{S3}

@@

As a stricter benchmark, we compared the quality of these
across-participant reconstructions (i.e., computed using a correlation
model derived from other patients' data) to reconstructions generated
using a correlation model trained using the in-patient's data.  In
other words, for this within-patient benchmark analysis we estimated
$\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in turn,
using recordings from all of that patient's electrodes except at the
location we were reconstructing.  These within-patient reconstructions
serve as an estimate of how well data from all of the other electrodes
from a single patient may be used to estimate held-out data.  This
allows us to ask how much information about the activity at a given
electrode might be inferred through (a) volume conductance or other
sources of ``leakage'' from activity patterns measured from the
patient's other electrodes and (b) across-electrode correlations
learned from that single patient.  As shown in
Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
within-patient correlations was centered well above zero (mean: XXX;
$t$-test comparing mean of distribution of $z$-transformed
per-electrode correlation coefficients to 0: $t(XXX) = XXX, p = XXX$).
However, the across-patient correlations were substantially higher
($t$-test comparing average $z$-transformed within versus across
patient electrode correlations: $t(XXX) = XXX, p = XXX$).  This is an
especially conservative test, given that the across-patient SuperEEG
reconstructions exclude (from the correlation matrix estimates) all
data from the patient whose data is being reconstructed.  We repeated
each of these analyses on a second independent datset and found
similar results (Fig.~\ref{fig:corrmap}B, D; within versus across
reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). Our finding,
that when reconstructing held-out data from a given patient
correlation models derived from \textit{other} patient's data yield
higher reconstruction accuracy than correlation models derived from
that patient, has two important implications.  First, it implies that
distant electrodes provide additional predictive power to the data
reconstructions beynd the information contained solely in nearby
electrodes.  (This follows from the fact that each patient's
electrodes are implanted in a unique set of locations, so for any
given electrode the closest electrodes in the full dataset are likely
to come from the same patient.)  Second, it implies that the spatial
correlations derived from the SuperEEG algorithm are, to some extent,
similar across people.

@@

@@

We were interested in the task specific contributions to the
reconstruction accuracy.  Each patient in the the second dataset
participated in two free recall experiments.  We ran similar analyses
for both experiments and found that activity was best reconstructed
when limiting the training data to within task, as opposed to across
task or incorporating data from both tasks (Fig.~\taskrecon (mean reconstruction accuracy incorporating data within task: 0.55, across task: 0.37, all tasks: .50)). Although reconstruction accuracy in the across task analysis was still better than the volume conductance model alone (paired $t$-test
between $z$-transformed mean correlation coefficients by patient: $t(47) = 5.65, p < 10\textsuperscript{-5}$), these results suggests that having a common tasks for patients may yield better reconstruction accuracy.

>>>>

\newcommand{\taskrecon}{S1}
\newcommand{\perexpcorrmaps}{S2}
\newcommand{\perexptaskrecon}{S3}
\newcommand{\perexptaskreconseparated}{S4}

@@

As a stricter benchmark, we compared the quality of these
across-participant reconstructions (i.e., computed using a correlation
model derived from other patients' data) to reconstructions generated
using a correlation model trained using the in-patient's data.  In
other words, for this within-patient benchmark analysis we estimated
$\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in turn,
using recordings from all of that patient's electrodes except at the
location we were reconstructing.  These within-patient reconstructions
serve as an estimate of how well data from all of the other electrodes
from a single patient may be used to estimate held-out data.  This
allows us to ask how much information about the activity at a given
electrode might be inferred through (a) volume conductance or other
sources of ``leakage'' from activity patterns measured from the
patient's other electrodes and (b) across-electrode correlations
learned from that single patient.  As shown in
Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
within-patient correlations was centered well above zero (mean: XXX;
$t$-test comparing mean of distribution of $z$-transformed
per-electrode correlation coefficients to 0: $t(XXX) = XXX, p = XXX$).
However, the across-patient correlations were substantially higher
($t$-test comparing average $z$-transformed within versus across
patient electrode correlations: $t(XXX) = XXX, p = XXX$).  This is an
especially conservative test, given that the across-patient SuperEEG
reconstructions exclude (from the correlation matrix estimates) all
data from the patient whose data is being reconstructed.  We repeated
each of these analyses on a second independent datset and found
similar results (Fig.~\ref{fig:corrmap}B, D; within versus across
reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). We also
replicated this result separately for each of the two experiments from
Dataset 2 (Fig.~\perexpcorrmaps).  This overall finding,
that when reconstructing held-out data from a given patient
correlation models derived from \textit{other} patient's data yield
higher reconstruction accuracy than correlation models derived from
that patient, has two important implications.  First, it implies that
distant electrodes provide additional predictive power to the data
reconstructions beynd the information contained solely in nearby
electrodes.  (This follows from the fact that each patient's
electrodes are implanted in a unique set of locations, so for any
given electrode the closest electrodes in the full dataset are likely
to come from the same patient.)  Second, it implies that the spatial
correlations derived from the SuperEEG algorithm are, to some extent,
similar across people.

@@

To test the task-specificity of the SuperEEG-derived correlation
models, we repeated our within- and across-patient cross validation
procedures separately for Experiment 1 and Experiment 2 data from
Dataset 2.  We then compared the reconstruction accuracies of held-out
electrodes, for models trained within versus across the two
experiments, or combining across both experiments
(Fig.~\perexptaskrecon).  In every case we found that across-patient
models trained using data from all other patients out-performed
within-patient models trained on data only from the subject
contributing the given electrode ($t$s$(XXX) > XXX, p$s$ < XXX$).  All
reconstruction accuracies also reliably exceeded chance performance
($t$s$(XXX) > XXX, p$s$ < XXX$).  Average reconstruction accuracy was
highest for the across-patient models limited to data from the same
experiment (mean accuracy: $0.55$), next-highest for the
across-patient models that combined data across both experiments (mean
accuracy: $0.50$), and lowest for models trained across task (mean
accuracy: $0.37$).  This result also held for each of the Dataset 2
experiments individually (Fig.~\perexptaskreconseparated).  Taken
together, these results indicate that there are reliable commonalities
in the spatial correlations of full-brain activity across tasks, but
that there are also reliable differences in these spatial correlations
across tasks.  Whereas reconstruction accuracy benefits from
incorporating data from other patients, reconstruction accuracy is
highest when constrained to within-task data, or data that includes a
variety of tasks (e.g., Dataset 1, or combining across the two Dataset
2 experiments).

@@
